### 2018-07-15 paper/message-passing-design.tex
WIP on SPOR section (fixes #46)

\NewScheme{\SPOR}{SPOR}
\NewScheme{\POR}{POR}

@@

\NewAlgorithm{\Send}{Send}
\NewAlgorithm{\Fwd}{Forward}
\NewAlgorithm{\Recv}{Receive}
\NewVariable{\rdv}{rdv}

We now describe a protocol \ac{SPOR}, which uses Sphinxes to transfer large 
messages from a source to a destination.
We provide the following algorithms:
\begin{itemize}
  \item \(\SPOR[\Send]\) (\cref{SPORSend}).
  \item \(\SPOR[\Fwd]\) (\cref{SPORFwd}).
  \item \(\SPOR[\Recv]\) (\cref{SPORRecv}).
\end{itemize}

Say that Alice wants to send a message \(m\) to Bob.
Bob runs the \(\SPOR[\Recv]\) algorithm and Alice runs the \(\SPOR[\Send]\) 
algorithm.
Bob (\ie \(\SPOR[\Recv]\)) creates a reply header using \(\CreateReply\) and 
gives the output to Alice (\ie \(\SPOR[\Send]\)) out-of-band.
At a later point, Alice attaches a message \(m\) to the reply header (using 
\(\UseReply\), creates a forward header using \(\CreateFwd\) with the prepared 
reply header as payload.
Then she send this packet to the first node, \ie invokes the \(\SPOR[\Fwd]\) 
algorithm on the first node.
The node will then process the header and in turn forward the packet to the 
next node.
When a node receives a packet where the nodes of the next layer is 
\(\{\rdvnode\}\), it will parse they payload as a packet to be forwarded.
When a node receives a packet where the nodes of the next layer is 
\(\{\nullnode\}\), then it knows that it is the intended recipient.

>>>>

\NewScheme{\SPOR}{SPOR}

@@

Say that Alice wants to send a message \(m\) to Bob.
Bob creates a reply header using \(\CreateReply\) and gives the output to Alice 
over an out-of-band channel.
We assume that \(m\) is either unavailable when the channel is used or too 
large to successfully send over the channel directly.
At a later point, Alice attaches a message \(m\) to the reply header using 
\(\UseReply\), creates a forward header using \(\CreateFwd\) with the prepared 
reply header as payload.
Then she sends this packet to the first node, which processes it using 
\(\ProcessHeader\).
The node will then process the header and in turn forward the packet to the 
next node.
At some point the message will reach Alice who identifies the message as the 
one expected to come from Bob.
In this section we will focus on how Alice and Bob choose the nodes that they 
provide to \(\CreateReply\) and \(\CreateFwd\).

There are many uses of Sphinxes, many criteria that can be used to select the 
nodes in each layer.
We will focus on maximizing availability when routing in a network with high 
churn.
But one could equally well select nodes to maximize, \eg, bandwidth.
We now describe a protocol, \ac{SPOR}, which uses Sphinxes to transfer messages 
from a source to a destination over a network of nodes with high churn.
